---
title: "Appendix D: Power Calculations for W241 Project"
author: "Venky, Christine, Jason"
date: "12/16/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(data.table)
library(pwr)
library(ggplot2)
```

# Power calculations for the Experiment only, Trial calculations are not included.  
  
## Reading data
```{r cars}
# Reading data set to include both Trial and Experiment
all_test <- fread('/Users/jasonabaker/W241/Final_Project/Data/Post_Experiment_Results.csv')

# Subsetting observations that were in the Experiment, Complied with the Treatment, Had valid test scores, and were from "Vijayawada, India".
ex_sub <- all_test[which(all_test$`Study Phase` == 'experiment' & all_test$`Treatment Outcome (Participated = 1, DNP = 0)` == 1 & all_test$Score_diff != 'NA' & all_test$Location == 'Vijayawada, India')]
```
  
  
## Subsetting _ex_sub_ into "Gaming", "Music", and "Reading".
```{r}
ex_1_game <- ex_sub[which(ex_sub$`Test Description` == "Gaming"),]
ex_1_music <- ex_sub[which(ex_sub$`Test Description` == "Reading"),]
ex_1_read <- ex_sub[which(ex_sub$`Test Description` == "Music"),]
```
  
  
## Calculate the overall mean and store it in a variable called grand_mean.
```{r}
grand_mean_1 <- round(mean(ex_sub$Score_diff), 2)
```
Grand Mean: `r grand_mean_1`  
  
  
## Calculating the mean score difference for each group.
```{r}
game_average_1 <- round(mean(ex_1_game$Score_diff),2)
music_average_1 <- round(mean(ex_1_music$Score_diff),2)
read_average_1 <- round(mean(ex_1_read$Score_diff),2)
```
Gaming Average:  `r game_average_1`  
Music Average:  `r music_average_1`  
Reading Average:  `r read_average_1`  
  
  
## Calculating the sample size of each group.
```{r}
sample_game_1 <- nrow(ex_1_game)
sample_music_1 <- nrow(ex_1_music)
sample_read_1 <- nrow(ex_1_read)
```
Gaming Sample Size: `r sample_game_1`  
Music Sample Size: `r sample_music_1`  
Reading Sample Size: `r sample_read_1`  
  

## Calculate the Between Group Variance
```{r}
between_group_variance_1 <- (sample_game_1 * (game_average_1 - grand_mean_1)^2 + sample_music_1 * (music_average_1 - grand_mean_1)^2 + sample_read_1 * (read_average_1 - grand_mean_1)^2) / 2
```
Between group variance: `r between_group_variance_1`  
  
  
## Calculate sum of squares for each group  
  + Used in _within_ _group_ _variance_
```{r}
sum_squares_game_1 <- sum((ex_1_game$Score_diff - game_average_1)^2) 
sum_squares_music_1 <- sum((ex_1_music$Score_diff - music_average_1)^2) 
sum_squares_read_1 <- sum((ex_1_read$Score_diff - read_average_1)^2) 
```
Gaming Sum of Squares:  `r sum_squares_game_1`  
Music Sum of Squares:  `r sum_squares_music_1`  
Reading Sum of Squares:  `r sum_squares_read_1`  
  
  
## Calculate the Within Group Variance
```{r}
within_group_variance_1 <- round((sum_squares_game_1 + sum_squares_music_1 + sum_squares_read_1) / (nrow(ex_sub) - 3), 0)
```
Within group variance: `r within_group_variance_1`  


# Power calculation  

## Power calculation (ANOVA) for current variances and sample sizes
```{r}
s_1 <- power.anova.test(groups = 3,
                        between.var = between_group_variance_1, within.var = within_group_variance_1,
                        power = NULL, sig.level = 0.05, n = 120.6)
s_1
```
  
  
  
# Iterated Power Calculation  
**We iterated through the power calculation to derive an understanding of our power relative to sample size.**  
  
## Setting n to loop through ANOVA calculation
```{r}
n_1 <- c(seq(2,10,by=1),seq(12,20,by=2),seq(25,200,by=25))
```
  
  
## Iterated power calculation
```{r}
p_1 <- power.anova.test(groups = 3,
                        between.var = between_group_variance_1, within.var = within_group_variance_1,
                        power = NULL, sig.level = 0.05, n=n_1)
```


```{r, echo=FALSE}
## Plotting power calculation  
plot(n_1,p_1$power, main = "One-way ANOVA Power", xlab = "Number of Observations", ylab = "Power")
abline(h = 0.8, v=121, col=c("blue","red"), lty=c(2,1), lwd=c(0.5,2))
#abline(v=c(13,450), col=c("red","blue"), lty=c(1,2), lwd=c(1,2))
```


