---
title: "Appendix F - Production Run Analysis for W241 Project"
author: "Venky, Jason, Christine"
output:
  rmarkdown::github_document
---

# 1. Setup 

```{r, message=FALSE}
library(data.table)
library(stargazer)
library(dplyr)
library(lmtest)
library(sandwich)
```


# 2. Analysis of Difference-in-Difference 
```{r}
din <- fread('./Post Experiment Results.csv', header = TRUE)
head(din)
```

```{r}
d <- din[which(din$`Study Phase` == 'experiment' & din$`Treatment Outcome (Participated = 1, DNP = 0)` == 1 & din$Score_diff != 'NA' & din$Location == 'Vijayawada, India')]
d <- d[, Treated := as.numeric(`Test Description` == "Gaming")]
d <- d[, Higher_grade := as.numeric(`Grade (or Age)` == 10)]
head(d)
```

```{r}
#Stargazer model with Robust SE
sgm_rse <-function(mod_name) {
  stargazer(
  mod_name, 
  type = 'text',
  se=list(sqrt(diag(vcovHC(mod_name))))
  )
} 
```

## 2.1 Simple model with treatment only
```{r}
dind_model_treat_only <- lm(Score_diff ~ Treated, d)
sgm_rse(dind_model_treat_only)
```

## 2.2 Model with treatment and covariates

```{r}
dind_model_with_covar <- lm(Score_diff ~ Treated + Gender + Higher_grade + `Time of Day Cat`, d)
sgm_rse(dind_model_with_covar)
```

## 2.3 Comparison of the base model for D-in-D with covariates

```{r}
stargazer(
  list(dind_model_treat_only, dind_model_with_covar),
  type = 'text',
  se=list(sqrt(diag(vcovHC(dind_model_treat_only))), sqrt(diag(vcovHC(dind_model_with_covar))))
  )
```

## 2.4 Simple model with Test Description
```{r}
dind_model_exp <- lm(Score_diff ~ `Test Description`, d)
sgm_rse(dind_model_exp)
```

## 2.5 With covariates
```{r}
dind_model_exp_with_covar <- lm(Score_diff ~ `Test Description` + Gender + Higher_grade + `Time of Day Cat` , d)
sgm_rse(dind_model_exp_with_covar)
```

## 2.6 Comparison of the base model for D-in-D with covariates

```{r}
stargazer(
  list(dind_model_exp, dind_model_exp_with_covar),
  type = 'text',
  se=list(sqrt(diag(vcovHC(dind_model_exp))), sqrt(diag(vcovHC(dind_model_exp_with_covar))))
  )
```


# 3. Analysis of post-test results only

## 3.1 Treatment only

```{r}
post_model_treat_only <- lm(`Post Score` ~ Treated, d)
sgm_rse(post_model_treat_only)
```

## 3.2 Treatment with covariates

```{r}
post_model_with_covar <- lm(`Post Score` ~ Treated + Gender + Higher_grade + `Time of Day Cat`, d)
sgm_rse(post_model_with_covar)
```


## 3.2 Treatment with Reading and Music

```{r}
post_model_exp <- lm(`Post Score` ~ `Test Description`, d)
sgm_rse(post_model_exp)
```

```{r}
post_model_exp_with_covar <- lm(`Post Score` ~ `Test Description` + Gender + Higher_grade + `Time of Day Cat`, d)
sgm_rse(post_model_exp_with_covar)
```


```{r}
pre_model_exp <- lm(`Pre Score` ~ `Test Description`, d)
sgm_rse(pre_model_exp)
```


```{r}
pre_model_exp_with_covar <- lm(`Pre Score` ~ `Test Description` + Gender + Higher_grade + `Time of Day Cat`, d)
sgm_rse(pre_model_exp_with_covar)
```

# 4. Analysis of pre-test results only

## 4.1 Treatment only

```{r}
pre_model_treat_only <- lm(`Pre Score` ~ Treated, d)
sgm_rse(pre_model_treat_only)
```

## 4.2 Treatment with covariates

```{r}
pre_model_with_covar <- lm(`Pre Score` ~ Treated + Gender + Higher_grade + `Time of Day Cat`, d)
sgm_rse(pre_model_with_covar)
```

## 5 Summary of pre and post models
```{r}
stargazer(
  list(pre_model_treat_only, pre_model_with_covar, post_model_treat_only, post_model_with_covar),
  type = 'text',
  se=list(sqrt(diag(vcovHC(pre_model_treat_only))), sqrt(diag(vcovHC(pre_model_with_covar))),
          sqrt(diag(vcovHC(post_model_treat_only))), sqrt(diag(vcovHC(post_model_with_covar)))
          )
  )
```

## 5.2 Average of pre, post and d-in-d scores

```{r}
nrow(d[d$`Test Description` == "Gaming"])
nrow(d[d$`Test Description` == "Reading"])
nrow(d[d$`Test Description` == "Music"])
```

```{r}
mean(d[`Test Description` == "Gaming",as.numeric(`Pre Score`)])
mean(d[`Test Description` == "Gaming",as.numeric(`Post Score`)])
```

# 6. Comparison against Music only and Reading only

```{r}
#Gaming and Music only
d_gm = d[d$`Test Description` == "Gaming" | d$`Test Description` == "Music"]
nrow(d_gm)
#Gaming and Reading only
d_gr = d[d$`Test Description` == "Gaming" | d$`Test Description` == "Reading"]
nrow(d_gr)
#Music and Reading only
d_mr = d[d$`Test Description` == "Music" | d$`Test Description` == "Reading"]
nrow(d_mr)
```

```{r}
dind_model_gaming_music <- lm(Score_diff ~ `Test Description` + Gender + Higher_grade + `Time of Day Cat` , d_gm)
dind_model_gaming_reading <- lm(Score_diff ~ `Test Description` + Gender + Higher_grade + `Time of Day Cat` , d_gr)
dind_model_music_reading <- lm(Score_diff ~ `Test Description` + Gender + Higher_grade + `Time of Day Cat` , d_mr)
stargazer(
  list(dind_model_gaming_music, dind_model_gaming_reading, dind_model_music_reading),
  type = 'text',
  se=list(sqrt(diag(vcovHC(dind_model_gaming_music))), sqrt(diag(vcovHC(dind_model_gaming_reading))), sqrt(diag(vcovHC(dind_model_music_reading))))
  )
```